wrangle

### 2025-04-29 wrangle.Rmd
added a script to simulate data for code checking purposes

>>>>

And this is the simulated data for code checking purposes, as the raw data cannot be made publicly available. 
If you have not requested the raw data privately, then uncomment the code chunk below and run the code.
See the sim_data.Rmd script for details on how the data were simulated. 
Note - the simulated data resemble the real data, but they will of course produce DIFFERENT results.

```{r}
# raw <- read_csv("data/simulated/sim_raw.csv")
# head(raw)
```
